### 2014-11-12 splash-bp.tex
rewording, use tightdescription

\begin{description}
   \item[Tree building]: Each node has a \texttt{inactive} fact that is used to
   start the tree building process. When the highest priority node is picked, a
   \texttt{tree} is created that will navigate through the tree. In lines 15-21,
   we use an \emph{aggregate}~\cite{cruz-iclp14} to gather all the neighbor
   nodes that have a positive priority (due to a new belief update) and are in the
   same thread. Nodes are collected into list \texttt{L} (line 21) and
   appended to list \texttt{Next}.

@@

   \item[Second phase]: In the second phase, the computation of beliefs is
   performed from the root to the leaves and the belief values are updated a
   second time (line 42).
\end{description}

Note that the \texttt{set-static} and \texttt{set-cpu} action fact are used in
line 2 in order to (1) force nodes to stay in the thread and (2) to partition
nodes as a grid of threads. This sets up a well defined area of nodes
for threads to build splash trees on.

@@

In this program, coordination assumes a far more important role than we have
seen before. Coordination rules fully drive the behavior of the algorithm and
although the final result of the algorithm is identical to the original
algorithm (minus probabilistic errors), SBP works in a very different way.
SBP is implemented in GraphLab~\cite{GraphLab2010}, a C++ framework for writing machine algorithms.
GraphLab provides the splash scheduler for these types of inferences as part of
the framework. This particular scheduler is around 350 lines of C++ code.
With our coordination facts, it is possible to create the necessary
patterns with only 12 simple rules.

>>>>

\begin{tightdescription}
   \item[Tree building]: Each node has a \texttt{inactive} fact that is used to
   start the tree building process. When the highest priority node is picked, a
   \texttt{tree} is created that will navigate through the tree. In lines 15-21,
   we use an \emph{aggregate}~\cite{cruz-iclp14} to gather all the neighbor
   nodes that have a positive priority (due to a new belief update) and are in the
   same thread. Nodes are collected into list \texttt{L} (line 21) and
   appended to list \texttt{Next}.

@@

   \item[Second phase]: In the second phase, the computation of beliefs is
   performed from the root to the leaves and the belief values are updated a
   second time (line 42).
\end{tightdescription}

The \texttt{set-static} and \texttt{set-cpu} action facts are used in
line 2 to (1) force nodes to stay in the thread and (2) 
partition nodes as a grid of threads. This sets up well defined areas
of nodes for threads to build splash trees on.

@@

In this program, coordination assumes a far more important role than
we have seen before. Coordination rules fully drive the behavior of
the algorithm and although the final result of the algorithm is
statistically identical to the original algorithm, SBP works very
differently than LBP.  SBP is also implemented in
GraphLab~\cite{GraphLab2010}, a C++ framework for writing machine
algorithms.  GraphLab provides the splash scheduler as part its the
framework. It is 350 lines of C++ code.  With our coordination facts,
it is possible to create the necessary scheduling with only 12 rules.
